Figures

### 2023-03-02 figures/figures.Rmd
clean up

```{r}
source("../scripts/99_utils.R")
```

```{r map}
print(2)
```

>>>>

```{r, echo=FALSE}
if(dir.exists("../scripts")){
    shim <- "../"
    source("../scripts/99_utils.R")
}else{
    shim <- ""
    source("scripts/99_utils.R")
}

```

```{r}
dt <- read.csv(
    paste0(shim, "../../Data/Euroflux/BE-Lon/L2-L4_2004-2012/EFDC_L2_Flx_BELon_2008_v017_30m.txt"),
    header = TRUE,
    colClasses = c("TIMESTAMP_START" = "character", "TIMESTAMP_END" = "character"),
    na.strings = "-9999") %>%
    clean_names()

head(dt)
```

```{r map}

coords_ire <- sf::st_as_sf(
    data.frame(lat = 50.45055, lon = 4.5350415),
    coords = c("lon", "lat"), crs = 4326)

dt_sites <- read.csv(
    system.file("extdata", "Site_metadata.csv", package = "FluxnetLSM")) %>%
    clean_names() %>%
    dplyr::mutate_all(na_if, "") %>%
    st_as_sf(coords = c("site_longitude", "site_latitude"), crs = 4326)

dt_dist <- unlist(st_distance(coords_ire, dt_sites))
dt_sites_close <- dt_sites[dt_dist < units::as_units(100, "mi"),]

rmarkdown::render_delayed({
    mapview(dt_sites_close) + mapview(coords_ire, color = "red")
    })
```
